Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-03-01 Supplemental-Material-B-Annotated-Analysis.Rmd
I

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "purrr"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

# dataframe where interaction types are recoded
studentInteractionType <- dtStudents$full %>%
  mutate(
    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
  ) %>%
  mutate(
    OutgroupInteraction = factor(
      InteractionDumDutch,
      levels = c(0, 1),
      labels = c("No", "Yes")
    ),
    NonOutgroupInteraction = factor(
      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
      levels = c(0, 1),
      labels = c("No", "Yes")
    )
  )

@@

df <-
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

>>>>

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate",
  "purrr",
  "metafor"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

@@

# dataframe where interaction types are recoded
studentInteractionType <- dtStudents$full %>%
  mutate(
    NonDutchContact = tidyr::replace_na(NonDutchContact, 2), # make second non-Dutch countable
    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
  ) %>%
  mutate(
    OutgroupInteraction = factor(
      InteractionDumDutch,
      levels = c(0, 1),
      labels = c("No", "Yes")
    ),
    NonOutgroupInteraction = factor(
      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
      levels = c(0, 1),
      labels = c("No", "Yes")
    )
  )

@@

medicalWithinBetween <-
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall",
        "OutgroupInteraction",
        "NonOutgroupInteraction"
      )
  )

df <- # keep only for compatibility of old framgents
  MlTraitState(
    data = df,
    id = "PID",
    selection =
      c(
        "KeyNeedFulfillment",
        "Competence",
        "Autonomy",
        "Relatedness",
        "AllportsCondition",
        "AttitudesDutch",
        "qualityOverall"
      )
  )

@@

# **Forest Plots of Main Analyses**

### Aggregate Data

summary of regression results from the aggregated contact and interaction quality data.

```{r metaGeneralLm, include=FALSE}
mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
                                mdlStudent$lmAttFreqQualX,
                                mdlMedical$lmAttFreqQualX)

lmMetaTbl <- data.frame()
for (i in 1:length(mdlTblElementsGeneralLm)){
  lmTblTmp <- lmTblPrep(mdlTblElementsGeneralLm[[i]])$coeficients %>%
  select(
    coef,
    B = est,
    se,
    lwr,
    upr,
    tval,
    Rsq
  ) %>%
  mutate(
    n = lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$N,
    m = nrow(.)-1, 
    sample = str_match(lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$data, "worker|student|medical"),
    coef = gsub(":", ".", coef)
  )
  lmMetaTbl <- rbind(lmMetaTbl, lmTblTmp)
}

lmMetaTbl <- lmMetaTbl %>% arrange(coef)

# extract parameter names
  name <- "Contact Hypothesis — Aggregate Linear Regression"
  var <- as.character(unique(lmMetaTbl$coef))[!as.character(unique(lmMetaTbl$coef)) %in% c("(Intercept)")]
  names <- qdap::mgsub(c("SumContactNL", "AvQuality", "SumContactNL.AvQuality"),
                       c("Number of Outgroup Contacts","Average Interaction Quality", "Contact X Quality"), 
                       var)
  studies <- as.character(unique(lmMetaTbl$sample))

### Parametric Meta-Analysis
    meta.parametric <- list()
    meta.parametric.sum <- data.frame(effect = var, 
                                      name = names, 
                                      beta.Worker = NA, 
                                      CI.Worker = NA,
                                      beta.Student = NA, 
                                      CI.Student = NA,
                                      beta.Medical = NA,
                                      CI.Medical = NA, 
                                      RE.beta = NA,
                                      RE.CI = NA,
                                      RE.pval = NA,
                                      RE.star = NA)

# i = 1
for(i in 1:length(var)){
      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var[i],],
                   measure = "SPCOR",
                   ti = tval,
                   ni = n,
                   mi = m,
                   r2i = Rsq,
                   var.names = c(paste(var[i],".yi",sep=""),paste(var[i],".vi",sep="")))

      meta.parametric[[var[i]]] <- rma(yi = get(paste(var[i],".yi",sep="")),
                                       vi = get(paste(var[i],".vi",sep="")), 
                                       data = md, 
                                       method = "FE", # "REML", 
                                       slab = sample)
      #metafor::forest(meta.parametric[[var[i]]],
      #                main = paste("Meta Analysis ",names[i],sep = ""))

      meta.parametric.sum$effect[i] <- var[i]
      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
      meta.parametric.sum$RE.CI[i] <- paste("[",
                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
}
    #meta.parametric

    eff <- escalc(data = lmMetaTbl, 
                  slab = coef,
                  measure = "SPCOR",
                  ti = tval,
                  ni = n,
                  mi = m,
                  r2i = Rsq)
    meta <- rma(yi = yi,
                vi = vi, 
                data = eff, 
                method = "FE", # "REML", 
                slab = paste(coef, sample, sep=" - "))

    k <- length(var) * length(studies)
    #png(file = "Figures/forestParametricGeneralLm.png", height = 200 + 40*k^.85) 
      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
      par(font=2)
      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
      m=1
      for(i in 3:1){
        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
        m <- m+6
      }
      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
    #dev.off()

### Bootstrapped Meta-Analysis
    var.boot <- var
    names.boot <- names
    meta.bootstrapped <- list()
    meta.bootstrapped.sum <- data.frame(effect = var.boot, 
                                      name = names.boot, 
                                      beta.Worker = NA, 
                                      CI.Worker = NA,
                                      beta.Student = NA, 
                                      CI.Student = NA,
                                      beta.Medical = NA,
                                      CI.Medical = NA, 
                                      RE.beta = NA,
                                      RE.CI = NA,
                                      RE.pval = NA,
                                      RE.star = NA)

    # i = 3
    for(i in 1:length(var.boot)){
      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var.boot[i],],
                   measure = "SPCOR",
                   yi = B,
                   sei = se,
                   ni = n,
                   mi = m,
                   var.names = c(paste(var.boot[i],".yi",sep=""),paste(var.boot[i],".vi",sep="")))

      meta.bootstrapped[[var.boot[i]]] <- rma(yi = get(paste(var.boot[i],".yi",sep="")),
                                              vi = get(paste(var.boot[i],".vi",sep="")),
                                              data = md,
                                              method = "FE",
                                              slab = sample)
      #metafor::forest(meta.bootstrapped[[var.boot[i]]],
      #                main = paste("Meta Analysis ",names.boot[i],sep = ""))
      meta.bootstrapped.sum$effect[i] <- var[i]
      meta.bootstrapped.sum$beta.Worker[i] <-
        meta.bootstrapped[[var[i]]]$yi[1]
      meta.bootstrapped.sum$beta.Student[i] <-
        meta.bootstrapped[[var[i]]]$yi[2]
      meta.bootstrapped.sum$beta.Medical[i] <-
        meta.bootstrapped[[var[i]]]$yi[3]
      meta.bootstrapped.sum$CI.Worker[i] <-
        paste(
          "[",
          round(meta.bootstrapped[[var[i]]]$yi[1] -
                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
          ", ",
          round(meta.bootstrapped[[var[i]]]$yi[1] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
          "]",
          sep = ""
        )
      meta.bootstrapped.sum$CI.Student[i] <-
        paste(
          "[",
          round(meta.bootstrapped[[var[i]]]$yi[2] -
                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
          ", ",
          round(meta.bootstrapped[[var[i]]]$yi[2] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
          "]",
          sep = ""
        )
      meta.bootstrapped.sum$CI.Medical[i] <-
        paste(
          "[",
          round(meta.bootstrapped[[var[i]]]$yi[3] -
                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
          ", ",
          round(meta.bootstrapped[[var[i]]]$yi[3] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
          "]",
          sep = ""
        )
      meta.bootstrapped.sum$RE.beta[i] <- meta.bootstrapped[[var[i]]]$b
      meta.bootstrapped.sum$RE.CI[i] <- paste(
        "[",
        round(meta.bootstrapped[[var[i]]]$ci.lb, 2),
        ", ",
        round(meta.bootstrapped[[var[i]]]$ci.ub, 2),
        "]",
        sep = ""
      )
      meta.bootstrapped.sum$RE.pval[i] <- meta.bootstrapped[[var[i]]]$pval
      meta.bootstrapped.sum$RE.star[i] <-
        ifelse(
          meta.bootstrapped.sum$RE.pval[i] < 0.001,
          "***",
          ifelse(
            meta.bootstrapped.sum$RE.pval[i] < 0.01,
            "**",
            ifelse(meta.bootstrapped.sum$RE.pval[i] < 0.05, "*", "")
          )
        )
    }
    #meta.bootstrapped

    eff.boot <- escalc(data = lmMetaTbl %>% filter(coef != "(Intercept)"), 
                       slab = coef,
                       measure = "SPCOR",
                       yi = B,
                       sei = se,
                       ni = n,
                       mi = m)
    meta.boot <- rma(yi = yi,
                     vi = vi, 
                     data = eff.boot, 
                     method = "FE", 
                     slab = paste(coef, sample, sep=" - "))

    k <- 3*3
    #png(file = "Figures/forestBootstrappedGeneralLm.png", height = 200 + 40*k^.85)
      metafor::forest(meta.boot, cex=0.75, xlim=c(-2, 2.5), ylim=c(-1, 20), rows=c(16:14,10:8,4:2), 
                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)),
                      mlab="", main=paste0("Meta Analysis: Forest Plot [Bootstrapped] \n(",name,")")) # , xlab = "Standardized Beta")
      par(font=2)
      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
      m=1
      for(i in 3:1){
        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
        m <- m+6
      }
      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
      text(2.5, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
    #dev.off()    
```

### Multilevel Analysis

summary of mixed models results of the contemporaneous contact effects.

```{r metaGeneralLmer, include=FALSE}
# lme
# Study 1: 
workerWithinBetween$AttitudesDutch <- workerWithinBetween$thermometerDutch_1
mdlWorker$lmerInterceptAttTypeTbl <- lmer(
    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
    data = workerWithinBetween
  )
workerWithinBetween$AttitudesDutch_zwc <- workerWithinBetween$thermometerDutch_1
mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + (1 | PID),
    data = workerWithinBetween
  )
# Study 2:
mdlStudent$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = studentWithinBetween
  )
mdlStudent$lmerSlopesAttTypeZ <- lmer(
    AttitudesDutch_zwc ~
      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
    data = studentWithinBetween
  )
# Study 3:
mdlMedical$lmerSlopesAttType <- lmer(
    AttitudesDutch ~
      OutgroupInteraction + NonOutgroupInteraction +
      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
    data = medicalWithinBetween
  )
mdlMedical$lmerSlopesAttTypeZ <- lmer(
    AttitudesDutch_zwc ~
      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
    data = medicalWithinBetween
  )

mdlTblElementsGeneralLmer <- list(
  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
  )

# i =1
GeneralLmerMetaTbl <- data.frame()
for (i in 1:length(mdlTblElementsGeneralLmer)){
  lmerTblTmp <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$beta %>%
  select(
    coef,
    B = est,
    se,
    lwr,
    upr,
    tval,
    Rsq
  ) %>%
  mutate(
    n = lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$N,
    m = nrow(.), 
    sample = str_match(lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$data, "worker|student|medical"),
    coef = gsub(":", ".", coef)
  )
  GeneralLmerMetaTbl <- rbind(GeneralLmerMetaTbl, lmerTblTmp)
}

GeneralLmerMetaTbl <- GeneralLmerMetaTbl %>% arrange(coef)

GeneralLmerMeta <- metaLmerOut(GeneralLmerMetaTbl,
                               type = "FE",
                               name = "GeneralLmer",
                               title = "Contact Hypothesis — Mixed Effects Regression")

# Alternative Meta:
      Metaan::estmeta(
        Beta = GeneralLmerMetaTbl$B[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        l = GeneralLmerMetaTbl$lwr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        u = GeneralLmerMetaTbl$upr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
        test = "FIXED", # "RANDOM"
      )
```

## Core Need Fulfillment

(a) Core Need Fulfillment predicting Interaction Quality.   
(b) Core Need Fulfillment predicting Outgroup Attitudes.   
(c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.

```{r metaTheory, include=FALSE}
# collect relevant models
# Study 1:
# Rename variables for consistency
tblDtS1Needs <- workerOutWithinBetween %>%
  select(
    Attitude = thermometerDutch_1,
    AttitudeZ = thermometerDutch_1_zwc,
    CoreNeed = keymotive_fulfillemt_1_cwc,
    CoreNeedZ = keymotive_fulfillemt_1_zwc,
    QualityRaw = quality_overall_1,
    Quality = quality_overall_1_cwc,
    QualityZ = quality_overall_1_zwc,
    PID = PID
  )
# Quality ~ CoreNeed
tblLmerS1QltInterceptCore <- lmer(
  QualityRaw ~ CoreNeed + (1 | PID),
  data = tblDtS1Needs
)
tblLmerS1QltInterceptCoreZ <- lmer(
  QualityZ ~ CoreNeedZ + (1 | PID),
  data = tblDtS1Needs
)
# Attitude ~ CoreNeed
tblLmerS1AttSlopeCore <- lmer(
  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
  data = tblDtS1Needs
)
tblLmerS1AttSlopeCoreZ <- lmer(
  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
  data = tblDtS1Needs
)
# Attitude ~ CoreNeed + Quality
tblLmerS1AttSlopeCoreQlt <- lmer(
  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
  data = tblDtS1Needs
)
tblLmerS1AttSlopeCoreQltZ <- lmer(
  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
  data = tblDtS1Needs
)

# Study 2:
# Rename variables for consistency
tblDtS2Needs <- studentOutWithinBetween %>%
  select(
    Attitude = AttitudesDutch,
    AttitudeZ = AttitudesDutch_zwc,
    CoreNeed = KeyNeedFullfillment_cwc,
    CoreNeedZ = KeyNeedFullfillment_zwc,
    QualityRaw = quality_overall,
    Quality = quality_overall_cwc,
    QualityZ = quality_overall_zwc,
    PID = PID
  )
# Quality ~ CoreNeed
tblLmerS2QltSlopesCore <- lmer(
  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
  data = tblDtS2Needs
)
tblLmerS2QltSlopesCoreZ <- lmer(
  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
  data = tblDtS2Needs
)
# Attitude ~ CoreNeed
tblLmerS2AttSlopesCore <- lmer(
  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
  data = tblDtS2Needs
)
tblLmerS2AttSlopesCoreZ <- lmer(
  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
  data = tblDtS2Needs
)
# Attitude ~ CoreNeed + Quality
tblLmerS2AttSlopesCoreQlt <- lmer(
  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
  data = tblDtS2Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)
tblLmerS2AttSlopesCoreQltZ <- lmer(
  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
  data = tblDtS2Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)

# Study 3:
# Rename variables for consistency
tblDtS3Needs <- medicalOutWithinBetween %>%
  select(
    Attitude = AttitudesDutch,
    AttitudeZ = AttitudesDutch_zwc,
    CoreNeed = KeyNeedFulfillment_cwc,
    CoreNeedZ = KeyNeedFulfillment_zwc,
    Allport = AllportsCondition_cwc,
    AllportZ = AllportsCondition_zwc,
    QualityRaw = qualityOverall,
    Quality = qualityOverall_cwc,
    QualityZ = qualityOverall_zwc,
    PID = PID
  )
# Quality ~ CoreNeed
tblLmerS3QltSlopesCore <- lmer(
  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
  data = tblDtS3Needs
)
tblLmerS3QltSlopesCoreZ <- lmer(
  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
  data = tblDtS3Needs
)
# Attitude ~ CoreNeed
tblLmerS3AttSlopesCore <- lmer(
  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
  data = tblDtS3Needs
)
tblLmerS3AttSlopesCoreZ <- lmer(
  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
  data = tblDtS3Needs
)
# Attitude ~ CoreNeed + Quality
tblLmerS3AttSlopesCoreQlt <- lmer(
  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
  data = tblDtS3Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)
tblLmerS3AttSlopesCoreQltZ <- lmer(
  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
  data = tblDtS3Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)
# Quality ~ Allport
tblLmerS3QltSlopesAllport <- lmer(
  QualityRaw ~ Allport + (1 + Allport | PID),
  data = tblDtS3Needs
)
tblLmerS3QltSlopesAllportZ <- lmer(
  QualityZ ~ AllportZ + (1 + AllportZ | PID),
  data = tblDtS3Needs
)
# Attitude ~ Allport
tblLmerS3AttSlopesAllport <- lmer(
  Attitude ~ Allport + (1 + Allport | PID),
  data = tblDtS3Needs
)
tblLmerS3AttSlopesAllportZ <- lmer(
  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
  data = tblDtS3Needs
)
# Attitude ~ Allport + Quality
tblLmerS3AttSlopesAllportQlt <- lmer(
  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
  data = tblDtS3Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)
tblLmerS3AttSlopesAllportQltZ <- lmer(
  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
  data = tblDtS3Needs,
  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
)
# Attitude ~ Allport + CoreNeed
tblLmerS3AttSlopesAllportCore <- lmer(
  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
  data = tblDtS3Needs
)
tblLmerS3AttSlopesAllportCoreZ <- lmer(
  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
  data = tblDtS3Needs
)

mdlTblElementsTheoryLmer <- list(
  # Study 1:
  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
  # Study 2:
  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
  # Study 3:
  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
  )

# i =1
theoryMetaTbl <- data.frame()
for (i in 1:length(mdlTblElementsTheoryLmer)){
  lmerTblTmp <- lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$beta %>%
  select(
    coef,
    B = est,
    se,
    lwr,
    upr,
    tval,
    Rsq
  ) %>%
  mutate(
    n = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$N,
    m = nrow(.), 
    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,".+?(?= ~)")),
    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$data, "S1|S2|S3")),
    formula = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,
    coef = gsub(":", ".", coef)
  )
  theoryMetaTbl <- rbind(theoryMetaTbl, lmerTblTmp)
}

theoryMetaTblNoAllport <- theoryMetaTbl %>%
  filter(!grepl("Allport",formula)) %>% 
  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
  arrange(formula, coef, sample)

TheoryMetaQualityNeed <-
  metaLmerOut(
    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
    type = "FE",
    name = "TheoryQualityCore",
    title = "Quality ~ CoreNeed"
  )

TheoryMetaAttitudeNeed <-
  metaLmerOut(
    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
    type = "FE",
    name = "TheoryAttitudeCore",
    title = "Attitude ~ CoreNeed"
  )

TheoryMetaAttitudeNeedQuality <-
  metaLmerOut(
    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
    type = "FE",
    name = "TheoryAttitudeCoreQuality",
    title = "Attitude ~ CoreNeed + Quality"
  )
```

## Robustness Analyses

(a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).  
(b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).

```{r metaRobust, include=FALSE}
# Full Sample
# Study 1:
robustTblWorkerFull <- 
  workerWithinBetween %>%
  select(
    AttitudesDutch = thermometerDutch_1,
    AttitudesDutch_zwc = thermometerDutch_1_zwc,
    CoreNeed_cwc = keyMotiveFulfilled_cwc,
    CoreNeed_zwc = keyMotiveFulfilled_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
    PID = PID
  )
mdlWorkerLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    data = robustTblWorkerFull
  )
mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    data = robustTblWorkerFull
  )
#Study 2:
robustTblStudentFull <- 
  studentWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFullfillment_cwc,
    CoreNeed_zwc = KeyNeedFullfillment_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
    PID = PID
  )
mdlStudentLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    data = robustTblStudentFull
  )
mdlStudentLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    data = robustTblStudentFull
  )
#Study 3:
robustTblMedicalFull <- 
  medicalWithinBetween %>%
  select(
    AttitudesDutch = AttitudesDutch,
    AttitudesDutch_zwc = AttitudesDutch_zwc,
    CoreNeed_cwc = KeyNeedFulfillment_cwc,
    CoreNeed_zwc = KeyNeedFulfillment_zwc,
    OutgroupInteraction = OutgroupInteraction,
    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
    PID = PID
  )
mdlMedicalLmerSlopesAttCoreInt <- lmer(
    AttitudesDutch ~
      CoreNeed_cwc * OutgroupInteraction +
      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
    #data = dtMedical$full
    data = robustTblMedicalFull
  )
mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
    AttitudesDutch_zwc ~
      CoreNeed_zwc * OutgroupInteraction_zwc +
      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
    #data = dtMedical$full
    data = robustTblMedicalFull
  )
